### 2018-05-12 msc_diploma_cubesat_galgoczi.tex
update

@@

\begin{figure}[H]
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\end{figure}

@@

\includegraphics[width=100.0mm]{images/satellite.png}

\includegraphics[width=150.0mm]{images/satellite_rad.png}

@@

\includegraphics[width=80.0mm]{images/positions.png}

>>>>

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

\begin{figure}
\includegraphics[width=130.0mm]{images/1channelelectronics.png}
\end{figure}

\begin{figure}
\includegraphics[width=130.0mm]{images/tap1channel.png}
\caption{\label{fig:1channeltape} The MPPC is fixed to the scintillator with valqua tape}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=130.0mm]{images/2channelsetup.png}
\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
\end{figure}

\includegraphics[width=130.0mm]{images/2channelelectronics.png}

\begin{figure}[H]
\centering
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
 \end{figure}

\begin{figure}
\includegraphics[width=150.0mm]{images/satellite_rad.png}
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=80.0mm]{images/positions.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator}
\end{figure}
